Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-11 paper/sections/metis-language-and-proofs.tex
[ paper ] translated the end of the metis subsection.

Una demostración de Metis para un problema logica propositional sin igualdad puede incluir en su derivacion \TSTP hasta 6 diferentes reglas de inferencia:
\canonicalize, \clausify, \conjunct, \negate, \simplify, y \strip.
Contrastando el codigo fuente de Metis y las reglas de la figura~\ref{fig:metis-inferences}. Podemos observar lo siguiente:
la regla de inferencia \emph{axiom} aparece por medio  de las reglas:
\canonicalize, \clausify, \conjunct, and \simplify.
La regla de inferencia \emph{resolve} aparece con el mismo nombre, \resolve.
Las ultimas reglas son \strip y \negate que son la representacion de la regla de inferencia \emph{assume}, las cuales sirven para
introducir en una demostracion la conjectura que se pretende demostrar, a esta conjetura nos referiremos tambien como el goal.
Toda prueba de un goal, tiene en su derivacion la negacion de dicho goal,
o de uno o varias proposiciones equivalentes, porque recordemos que
las pruebas son por refutacion.

De esta manera concluimos con una breve descripcion del probador de teoremas Metis. En lo siguiente, intentaremos justificar derivación de Metis paso por paso. Para esto,estudiamos cada una de las reglas antes mencionadas en más detalle, y para cada una de ellas, proponemos un teorema para emular
su  razonamiento.

>>>>

A proof derivation reply by \Metis for a classic propositional logic
without equality include in the \TSTP file at least six different inferences rules. These are exactly the same six rules from the
\Metis's description in Fig.~\ref{fig:metis-inferences}. The aforementioned rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
Based on the scope of the problems (CPL) but also from the list of 6 inferences rules described on the \Metis' documentation, only 3 rules can be applied: \emph{axiom}, \emph{assume} and \emph{resolve}.

Comparing these rules with \TSTP derivations but also after looking at the
\Metis' source code, we speculate to say that for example.
The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} appears using the
same name with the binary rule \resolve. The \emph{assume} rule is the inference rule \negate to introduce the negation of the conjecture since
\Metis replies refutation proofs. The \strip rule works with the conjecture, also named as the \emph{goal} of the problem. This intends for finding a equivalent conjunction of easier or smaller in size propositions, named \emph{subgoals}.

This section briefly describes the \Metis prover for our purposes.
In the next section, we discuss the proof-reconstruction for \Metis \TSTP derivations. In addition, we show a more detailed discussion around
the aforementioned proof rules.

### 2017-10-11 paper/sections/proof-reconstruction.tex
[ paper ] translated the end of the metis subsection.

% The proof-reconstruction approach proposed here consists of a series
% of steps similar to the workflow presented by \citeauthor{sultana2015} in
% \cite{sultana2015}. This process is a translation from a source
% system to a target system. In our case, the system of origin, the
% automatic theorem prover, is \Metis; the target system is a proof
% assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
% Section~\ref{sec:implementation}).
% The overview of the proof-reconstruction is presented in
% Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
% a problem in \CPL that we encode in \TPTP format to be sent as the
% input of the \Metis prover.
% The algorithms of \Metis in Step~3 find
% a solution if the problem is a theorem, in that case \Metis replies
% with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.

>>>>

The proof-reconstruction approach proposed here consists of a series
of steps similar to the workflow presented by \citeauthor{sultana2015} in
\cite{sultana2015}. This process is a translation from a source
system to a target system. In our case, the system of origin, the
automatic theorem prover, is \Metis; the target system is a proof
assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
Section~\ref{sec:implementation}).
The overview of the proof-reconstruction is presented in
Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
a problem in \CPL that we encode in \TPTP format to be sent as the
input of the \Metis prover.
The algorithms of \Metis in Step~3 find
a solution if the problem is a theorem, in that case \Metis replies
with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
